% ============================================================
%  WeldVision X5 – Executive Summary
%  Compile with: pdflatex EXECUTIVE_SUMMARY.tex
% ============================================================
\documentclass[11pt,a4paper]{article}

% --- Packages ---
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2.8cm, right=2.8cm]{geometry}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{array}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\usepackage{caption}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{tikz}

% --- Colours ---
\definecolor{darkblue}{RGB}{26,58,92}
\definecolor{medblue}{RGB}{46,109,164}
\definecolor{lightblue}{RGB}{212,230,241}
\definecolor{darkgray}{RGB}{51,51,51}
\definecolor{accentorange}{RGB}{200,100,0}

% --- Font ---
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% --- Section styling ---
\usepackage{titlesec}
\titleformat{\section}
  {\large\bfseries\color{darkblue}}
  {}
  {0pt}
  {\colorbox{lightblue}{\parbox{\dimexpr\linewidth-2\fboxsep}{\strut\hspace{4pt}#1\strut}}}
\titlespacing{\section}{0pt}{14pt}{6pt}

% --- Line spacing ---
\setstretch{1.2}

% --- Header / Footer ---
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\itshape\color{darkgray} WeldVision X5 -- Executive Summary}
\fancyhead[R]{\small\itshape\color{darkgray} Politeknik Kuching Sarawak}
\fancyfoot[C]{\small\color{darkgray}\thepage}
\renewcommand{\headrulewidth}{0.5pt}

% --- Column types ---
\newcolumntype{L}[1]{>{\RaggedRight\arraybackslash}p{#1}}

% ============================================================
\begin{document}
% ============================================================

% ── Title Banner ─────────────────────────────────────────────
\begin{center}
  \begin{tikzpicture}
    \fill[darkblue] (0,0) rectangle (\textwidth, 2.4cm);
    \node[white, font=\LARGE\bfseries, anchor=center] at (0.5\textwidth, 1.5cm)
      {WeldVision X5};
    \node[white, font=\normalsize, anchor=center] at (0.5\textwidth, 0.7cm)
      {Automated Vision-Based Evaluation of Student SMAW Welding Coupons};
  \end{tikzpicture}

  \vspace{6pt}
  {\normalsize\bfseries\color{darkblue} Politeknik Kuching Sarawak}\\[2pt]
  {\small Department of Mechanical Engineering \quad|\quad Date: 14 May 2026}
\end{center}

\vspace{8pt}

% ── Problem Statement ────────────────────────────────────────
\section{Problem Statement}

Assessment of student Shielded Metal Arc Welding (SMAW) coupons is currently \textbf{manual, subjective, and
time-consuming}. It produces no permanent digital record, lacks consistency between assessors, and does not
leverage Industry~4.0 technologies to improve learning outcomes. Instructors spend considerable time per
coupon using physical gauges and visual checklists, leaving little capacity for targeted student feedback.

% ── Proposed Solution ───────────────────────────────────────
\section{Proposed Solution}

\textbf{WeldVision X5} is an Industry~4.0 prototype that automates the entire evaluation workflow. A
low-cost \textbf{RDK~X5} edge device with a stereo camera, mounted on a repurposed Ender~3 motion rig,
captures images of the welded coupon. On-device AI (YOLOv8s on the BPU) detects surface defects, while
classical stereo vision (SGBM on the CPU) extracts 3D geometry -- weld width, reinforcement height, and
undercut depth. These measurements are fed into a digital rubric that mirrors the institution's grading
criteria, generating a scored assessment in approximately 8 seconds.

All results are synchronised to a serverless Cloudflare backend and displayed on a responsive React
dashboard, which includes:
\begin{itemize}[leftmargin=1.5em, itemsep=3pt]
  \item An interactive \textbf{3D point-cloud viewer} for visual inspection of weld geometry.
  \item A \textbf{manual rejection mechanism} for instructors to flag suspected internal defects (e.g., lack
        of fusion) that surface vision cannot detect -- triggering a mandatory physical test.
  \item \textbf{Historical analytics} for tracking student progress over time.
\end{itemize}

The entire cloud pipeline (Roboflow, Google Colab, Cloudflare, GitHub Actions) operates within
\textbf{free-tier limits}, with hardware costs of approximately USD~\$150.

% ── Key Results ─────────────────────────────────────────────
\section{Key Results}

\begin{center}
\begin{tabular}{L{5.5cm} L{9cm}}
  \toprule
  \textbf{Metric} & \textbf{Result} \\
  \midrule
  Detection accuracy & mAP@0.5 = \textbf{0.92}; per-class F1 = 0.86--0.92 across four defect classes \\
  \addlinespace
  Geometric accuracy (RMSE) &
    Weld width: $<0.4$\,mm \quad
    Reinforcement: $<0.3$\,mm \quad
    Undercut: $<0.1$\,mm \\
  \addlinespace
  Rubric correlation & Pearson's $r = 0.87$ vs.\ average of three human assessors ($n = 50$) \\
  \addlinespace
  Inspection speed   & $\approx 8$ seconds per coupon (5 stereo pairs) \\
  \addlinespace
  Hardware cost      & $\approx$ USD \$150 (RDK~X5 + camera + repurposed Ender~3 frame) \\
  \addlinespace
  Cloud cost         & \$0 (free-tier: Roboflow, Google Colab, Cloudflare, GitHub Actions) \\
  \addlinespace
  Edge power draw    & 7.8\,W (RDK~X5), $\approx$30\,W total station \\
  \bottomrule
\end{tabular}
\end{center}

\vspace{6pt}
\noindent\textbf{Manual rejection effectiveness:} Instructors flagged 6 of 50 coupons (12\%) where automated
scores appeared acceptable but point-cloud geometry suggested internal bonding issues. Macro-etch examination
confirmed lack of fusion in 4 of those 6 cases, validating the hybrid human-AI approach.

% ── IR 4.0 & Sustainability ─────────────────────────────────
\section{IR~4.0 Alignment \& Sustainability}

\begin{minipage}[t]{0.48\textwidth}
\textbf{\color{medblue}IR~4.0 Pillars Addressed}
\begin{itemize}[leftmargin=1.2em, itemsep=3pt]
  \item \textbf{Interconnectivity:} Edge device syncs inspection data to Cloudflare cloud in real time via
        LAN/Wi-Fi; offline-first buffering ensures no data loss.
  \item \textbf{Information transparency:} All assessments are centrally logged in D1 with full traceability;
        instructors view consolidated dashboards.
  \item \textbf{Technical assistance:} AI grades surface quality, provides Likert-scored criterion breakdown,
        and suggests grade band with actionable feedback for students.
  \item \textbf{Decentralised decisions:} Edge device operates autonomously in the workshop without requiring
        cloud connectivity for each inspection cycle.
\end{itemize}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\textbf{\color{medblue}Sustainability Features}
\begin{itemize}[leftmargin=1.2em, itemsep=3pt]
  \item \textbf{Hardware reuse:} Ender~3 printer frame repurposed as gantry, reducing e-waste.
  \item \textbf{Low power:} BPU+CPU architecture consumes $<10$\,W; no GPU server required.
  \item \textbf{Paperless:} Digital rubrics replace physical checklists and paper records.
  \item \textbf{Free-tier cloud:} Zero operational cloud cost; no server provisioning or maintenance.
  \item \textbf{Scalable:} Multi-booth deployment with a single cloud backend incurs no incremental cost.
\end{itemize}
\end{minipage}

% ── Conclusion ──────────────────────────────────────────────
\section{Conclusion}

WeldVision~X5 proves that a fully automated, reliable, and cost-effective digital welding assessment system
is feasible for educational institutions with limited budgets. By combining on-device AI (YOLOv8s on BPU)
with classical stereo depth estimation (SGBM on CPU) and a free-tier serverless cloud backend, the prototype
delivers objective, consistent, and traceable assessment of student SMAW coupons at approximately
\$150 hardware cost and zero cloud cost.

The system enhances learning through granular Likert-scored feedback, reduces instructor workload by
automating routine surface grading, and preserves human judgment for internal defect detection via the manual
rejection mechanism. It demonstrates a practical, scalable template for IR~4.0 integration in vocational
technical education and aligns with sustainability goals through hardware reuse, low power consumption, and
paperless digital records.

\vspace{16pt}
\noindent\rule{\linewidth}{0.8pt}
{\small\color{darkgray}
\textit{WeldVision X5} $\cdot$ Politeknik Kuching Sarawak, Department of Mechanical Engineering $\cdot$
\url{https://weldvision-x5.com}
}

\end{document}
